--- 
title: "Open Music Europe Template"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
   word_document:
    reference_docx: "document/Open_Music_Europe_Document.docx"
   bookdown::gitbook:
     default
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write use the templated designed by Synyo. "
---

# Prerequisites

This is a _sample_ book written in **Markdown** and the Word document template provided by **Synyo**. We simply loaded the template into the  [bookdown](https://github.com/rstudio/bookdown). [minimal example](https://github.com/rstudio/bookdown-demo) after some errors (removing Microsoft-only fonts.)

You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
